The \kepler Smear Campaign I: An Asteroseismic Catalogue of Bright Red Giants

### 2018-08-10 paper/ms.tex
reformat
subsubsection

\subsection{Chemical Composition}
\label{chemical}
place [X/Fe] vs [Fe/H] diagrams here and discuss which Galactic populations these stars come from. May also want to discuss how these span the typical Galactic populations and can act as benchmark stars for APOGEE or other large surveys

\subsection{Red Clump Stars}
\label{clumpstars}

@@

\subsection{Classical Pulsators}
\label{pulsators}

Two stars in the sample show the `hump-and-spike' morphology in their power spectra (a broad `hump' of low-amplitude oscillations dominated by one high amplitude coherent oscillation): HD~186155 (HR~7495), and HD~183362 (HR~7403), respectively the third brightest and $37^{\text{th}}$-brightest stars on silicon and the brightest two stars that show this effect. Another star with a hump-and-spike spectrum is Boyajian's~Star, which shows deep enigmatic dips in brightness \citep{2016MNRAS.457.3988B}, and has faded both throughout the \kepler mission \citep{2016ApJ...830L..39M} and in relation to Harvard photographic plates from 1890 onwards \citep{2016ApJ...822L..34S}. The dimming, which is chromatic in the manner expected of heterogeneous clouds of circumstellar dust in the line of sight \citep{2018ApJ...853..130D,2018arXiv180608842B}, has been ascribed to various causes \citep[reviewed in][]{2018RNAAS...2a..16W}, most notably a cloud of exocomets surrounding the star \citep[e.g.][]{2018MNRAS.473.5286W}. It is unclear whether the explanation of the hump-and-spike phenomenon will shed light on the strange behaviour of Boyajian's~Star, but it may be relevant.
\citet{2018MNRAS.474.2774S} have recently claimed the hump-and-spike power spectra as evidence for Rossby modes. The F5 star HD~186155, identified by SIMBAD as having a giant spectral type of F5II-III, is shown by its \gaia distance to in fact lie on the main sequence. The other example is the B3e star HD~183362 at $G = -2.576$. A detailed study of these stars will be presented by Antoci et al., in prep.

@@

We believe in open science, and have therefore made all substantive products of this research available to the interested reader. All code used to produce smear light curves is available under a GPL~v3 license at \url{github.com/benjaminpope/keplersmear}. All smear light curves, both including the red giant sample studied in detail in Section~\ref{rgs}, and other stars as discussed in Section~\ref{other}, can be downloaded from the Mikulski Archive for Space Telescopes (MAST) as a High-Level Science Product. TRES spectra are available from \textcolor{red}{somewhere}, and all asteroseismic parameters and derived stellar parameters for the red giants in Section~\ref{rgs} are provided in an online-only table as Supplementary Material to this paper.

>>>>

\subsubsection{Chemical Composition}
\label{chemical}
place [X/Fe] vs [Fe/H] diagrams here and discuss which Galactic populations these stars come from. May also want to discuss how these span the typical Galactic populations and can act as benchmark stars for APOGEE or other large surveys

\subsubsection{Red Clump Stars}
\label{clumpstars}

@@

\subsection{Main Sequence Pulsators}
\label{pulsators}

Two stars in the sample show the `hump-and-spike' morphology in their power spectra (a broad `hump' of low-amplitude oscillations dominated by one high amplitude coherent oscillation): HD~186155 (HR~7495), and HD~183362 (HR~7403), respectively the third brightest and $37^{\text{th}}$-brightest stars on silicon and the brightest two stars that show this effect. \citet{2018MNRAS.474.2774S} have recently claimed the hump-and-spike power spectra as evidence for Rossby modes. The F5 star HD~186155, identified by SIMBAD as having a giant spectral type of F5II-III, is shown by its \gaia distance to in fact lie on the main sequence. The other example is the B3e star HD~183362 at $G = -2.576$. A detailed study of these stars will be presented by Antoci et al., in prep.

Another star with a hump-and-spike spectrum is Boyajian's~Star, which shows deep enigmatic dips in brightness \citep{2016MNRAS.457.3988B}, and has faded both throughout the \kepler mission \citep{2016ApJ...830L..39M} and in relation to Harvard photographic plates from 1890 onwards \citep{2016ApJ...822L..34S}. The dimming, which is chromatic in the manner expected of heterogeneous clouds of circumstellar dust in the line of sight \citep{2018ApJ...853..130D,2018arXiv180608842B}, has been ascribed to various causes \citep[reviewed in][]{2018RNAAS...2a..16W}, most notably a cloud of exocomets surrounding the star \citep[e.g.][]{2018MNRAS.473.5286W}. It is unclear whether the explanation of the hump-and-spike phenomenon will shed light on the strange behaviour of Boyajian's~Star, but it may be relevant.

@@

We believe in open science, and have therefore made all substantive products of this research available to the interested reader. All code used to produce smear light curves is available under a GPL~v3 license at \url{github.com/benjaminpope/keplersmear}. All smear light curves, both including the red giant sample studied in detail in Section~\ref{rgs}, and main sequence stars as discussed in Sections~\ref{pulsators} and~\ref{ebs}, can be downloaded from the Mikulski Archive for Space Telescopes (MAST) as a High-Level Science Product. TRES spectra are available from \textcolor{red}{somewhere}, and all asteroseismic parameters and derived stellar parameters for the red giants in Section~\ref{rgs} are provided in an online-only table as Supplementary Material to this paper.
